### 2020-01-31 S2_appendix.tex
Benchmarking

@@

\begin{figure}[!htb]
%\includegraphics[width=0.85\textwidth]{Figures/CalSim_quant.pdf}
\caption{\textbf{Bactrian proposal kernel.} A $\text{Bactrian}(0.95)$ proposal kernel is used for all clock model operators, as described in main article.}
\end{figure}

>>>>

\begin{figure}[!htb]
\includegraphics[width=0.85\textwidth]{Figures/CalSim_bactrian95.pdf}
\caption{\textbf{Bactrian proposal kernel.} A $\text{Bactrian}(0.95)$ proposal kernel is used for all clock model operators (under \textit{quant}), as described in main article.}
\end{figure}

@@
